% last updated in April 2002 by Antje Endemann
% Based on CVPR 07 and LNCS, with modifications by DAF, AZ and elle, 2008 and AA, 2010, and CC, 2011; TT, 2014; AAS, 2016

\documentclass[runningheads]{llncs}
\usepackage{graphicx, hyperref}
\usepackage{amsmath,amssymb} % define this before the line numbering.
\usepackage{ruler}
\usepackage{color}
\usepackage[width=122mm,left=12mm,paperwidth=146mm,height=193mm,top=12mm,paperheight=217mm]{geometry}

\graphicspath{{figs/}}

\newcommand{\red}[1]{\textcolor{red}{#1}}

\begin{document}
% \renewcommand\thelinenumber{\color[rgb]{0.2,0.5,0.8}\normalfont\sffamily\scriptsize\arabic{linenumber}\color[rgb]{0,0,0}}
% \renewcommand\makeLineNumber {\hss\thelinenumber\ \hspace{6mm} \rlap{\hskip\textwidth\ \hspace{6.5mm}\thelinenumber}}
% \linenumbers
\pagestyle{headings}
\mainmatter
\def\ECCV18SubNumber{***}  % Insert your submission number here

\title{ClassificationCam: How can optics be used in convolutional neural networks? (not final)} % Replace with your title

\titlerunning{ECCV-18 submission ID \ECCV18SubNumber}

\authorrunning{ECCV-18 submission ID \ECCV18SubNumber}

\author{Anonymous ECCV submission}
\institute{Paper ID \ECCV18SubNumber}


\maketitle

\begin{abstract}
The abstract should summarize the contents of the paper. LNCS guidelines
indicate it should be at least 70 and at most 150 words. It should be set in 9-point
font size and should be inset 1.0~cm from the right and left margins. Paper page limit is 14 pages, excluding references.

\keywords{We would like to encourage you to list your keywords within
the abstract section}
\end{abstract}


\section{Introduction, pp. 1-2}
\label{sec:intro}
% \input{sections/introduction}

CNNs are very important, but they require a lot of computation. Optics can offer passive, fast, highly parallel computation. This project explores incorporating optical computing in convolutional neural networks. We present several models and assess their limitations and potential.

\section{Related Work, pp. 2-4}
\label{sec:related}
\input{sections/related}


\section{ONN Toolbox, pp. 5-7}
\label{sec:toolbox}
In this section we present building blocks for an optically implemented CNN. In this rest of this paper we focus on the convolutional layer, but we will briefly discuss other layers here too.
\begin{itemize}
\item Convolutional layer:
	Small kernel, tiled kernels, single large kernel (\red{Fig. 1})
\item Other layers that we didn’t test in detail: \\
Optical nonlinearities \\ 
	Max/avg pooling with spectral pooling \\ 
	Fully connected layers	
\end{itemize}

\section{Training, pp. 7}
Here we talk about how we train the ONN offline in Tensorflow. PSF optimization followed by phase mask optimization OR end-to-end phase mask optimization.

\section{Simulations, pp. 8-10}
\label{sec:simulation}
We use simulations to better understand the performance of optical CNNs. \\
\red{Fig. 2}: diagram of possible ONN models.
\red{Table 1:} Results.
\begin{itemize}
\item Introduce toy classification problem(s?), discuss constraints.
\item Learned optical correlator (single optical conv. layer) \\ Here we are able to use end-to-end learning. \\
\red{Possible figure with learned phase mask and PSF.}
\item Hybrid optoelectronic (one optical conv. layer)\\ 
	Talk about the dual channel positive and negative weights\\
	Grayscale \\
	With color filters – \red{Vincent?}\\
\red{Fig. 3: Hybrid ONN phase masks and PSFs.}
\item All-optical convolutional neural network \\
Doesn’t fully work, but can discuss some results
\end{itemize}

\section{Optical Prototype, pp. 10-11}
\label{sec:prototype}
Implement the hybrid optoelectronic two-layer neural network. Goal is to show that the hybrid ONN can perform on par with the electronic ONN, with the same number of layers, and better than the electronic ONN with one fewer layer.\\
\red{Fig. 4: optical setup} \\
\red{Fig. 5: actual PSF and sample images} \\
\red{Table. 2: results}

\section{Discussion, pp. 12-13}
\label{sec:discussion}
\begin{itemize}
\item Not straightforward to generalize first optical conv. layer to multiple optical layers
\item Discuss importance of negative weights – \red{Vincent?}
\item Instead of trying to replicate a CNN exactly, could take advantage of optical transformations that aren't as practical in computations. For example, we use a 4f system for convolution, but this requires two extra lenses. Perhaps a single custom learned optical element can be used instead.
\item In the future, exploit other properties of light (polarization, phase)	
\item Specifically, coherent light and holography, photonics
\end{itemize}

\section{Conclusion, p. 14}
\label{sec:conclusion}
\input{sections/conclusion}

\clearpage

\bibliographystyle{splncs}
\bibliography{../bibliography}
\end{document}
